\documentclass[12pt]{article}


\usepackage[margin=2cm]{geometry}
\usepackage[shortlabels]{enumitem}
\usepackage{amsmath,amsxtra,amsthm,amssymb,mathrsfs}

\usepackage{exsheets}
\SetupExSheets{headings=runin}
\SetupExSheets{question/type=exercise}
\SetupExSheets{question/name=Ex }


\DeclareMathOperator{\moduleCategory}{\mathsf{mod}} \renewcommand{\mod}{\moduleCategory}

\newcommand{\Hom}{\operatorname{Hom}\nolimits}
\newcommand{\End}{\operatorname{End}\nolimits}

\DeclareMathOperator{\Char}{char}
\newcommand{\triv}{\operatorname{triv}\nolimits}
\newcommand{\sgn}{\operatorname{sgn}\nolimits}
\newcommand{\Mat}{\operatorname{Mat}\nolimits}
\newcommand{\GL}{\operatorname{GL}\nolimits}
\DeclareMathOperator{\Sn}{\mathfrak{S}}
\newcommand{\Res}{\operatorname{Res}\nolimits}
\newcommand{\Ind}{\operatorname{Ind}\nolimits}

\begin{document}

{\scshape Autumn 2022} \hfill {\scshape \large Topics in Math. Sci. IV} \hfill {\scshape Homework Assignment 2}
\smallskip

\hrule

\bigskip


\begin{question}
Let $A$ be a $K$-algebra.
\begin{enumerate}
\item Show that $Z(A)\cong \End_{A\otimes_K A^{\mathrm{op}}}(A)$ as rings.

\item Suppose $A=B\times B'$ for some $K$-algebras $B,B'$ (in this case, call $B$ and $B'$ the direct factors of $A$).  Show that the identity $1_B$ is a central idempotent of $A$, i.e. an element $b\in Z(A)$ with $b^2=b$.

\item Show that $B$ is a direct factor of $A$ if, and only if, $A\cong B\oplus B'$ as $A\otimes_K A^{\mathrm{op}}$-module.

\item Show that $B$ is a direct factor of $KG$ if, and only if, $B$ is a direct summand of $K(G\times G)$.
\end{enumerate}
\end{question}

\begin{question}
For $V,W\in KG\mod$, show that there are the following isomorphisms.
\begin{enumerate}
\item $(V\otimes_KW)^*\cong V^*\otimes_K W^*$ as $KG$-modules.
\item $V^* \otimes_K W \cong \Hom_K(V,W)$ as $KG$-modules.
\end{enumerate}
\end{question}

%\begin{question}
%Suppose $X$ is a $G$-set (i.e. $G$ acts by permuting elements of $X$) or a $KG$-module, denote by $X^G$ the invariant subspace $\{x\in X\mid gx=x \,\forall g\in G\}$ of $X$.
%Let $U,V,W\in KG\mod$.
%\begin{enumerate}
%\item Show that $(V^*\otimes_K V)^G \cong \End_{KG}(V)$.
%\item Show that $\Hom_{KG}(U\otimes_KV, W)\cong \Hom_{KG}(U, V^* \otimes_K W)$
%\end{enumerate}
%\end{question}

\begin{question}
Recall that $\End_K(V)$ is a ring where multiplication is composition.
\begin{enumerate}
\item Find the multiplication on $V^*\otimes_K V$ that makes $\End_K(V)\cong V^*\otimes_K V$ an isomorphism of rings.

\item Suppose $V\in KG\mod$.  Show that $\triv_G$ is a direct summand of $V^*\otimes_K V$ when $\dim_K M$ is invertible in $K$.  (Hint: fix a basis of $V$ and consider also the dual basis.)
\end{enumerate}
\end{question}

\begin{question}
Suppose $H\leq G$ is a subgroup.
For $g\in G$, let ${}^gH:=gHg^{-1}=\{{}^gh:=ghg^{-1}\mid h\in H\}$, and define for each $KH$-module $W$ a $K({}^gH)$-module ${}^gW:=\{{}^gw\mid w\in W\}$ (${}^gw$ is just a formal symbol) with ${}^gh\cdot w:= {}^g(hw)$.
Show that 
\begin{enumerate}
\item $\Ind_{{}^gH}^G ({}^g W) \cong \Ind_H^G(W)$ as $KG$-module;
\item ${}^gV \cong V$ as $KG$-module for all $V\in KG\mod$.
\end{enumerate}
\end{question}

\begin{question}
Let $H\leq G$, $V\in KG\mod$ and $W\in KH\mod$.  Show that
\begin{enumerate}
\item $V\otimes_K \Ind_H^G(W) \cong \Ind_H^G(\Res_H^G(V)\otimes_KW)$;
\item $\Ind_H^G (W^*) \cong (\Ind_H^G(W))^*$;
\item use (2) to give an alternative proof of permutation module being self-dual.
\end{enumerate}
\end{question}

\begin{question}
Consider an integer $n\geq 1$ and an integer $r\leq n/2$.  Let $\Omega_r$ be the set of $r$-subsets (=subsets of size $r$) of $\{1,2,\ldots, n\}$.
\begin{enumerate}
\item Find (and prove) a subgroup $H\leq \Sn_n$ such that $K\Omega_r \cong \Ind_H^{\Sn_n}\triv_H$.

\item Let $\pi_r$ be the character of $K\Omega_r$.  Find $\pi_r(1)$.  (Note: $\chi_{K\Omega}(g)=|\{\omega\in \Omega\mid g\omega =\omega\}$ for any $G$-set $\Omega$.)
\end{enumerate}
\end{question}



\vfill
\hfill Deadline: 22nd November, 2022


\end{document}